\title{A grammar of Moloko}  
\BackTitle{A grammar of Moloko} % Change if BackTitle != Title
\BackBody{Mana Samuel, Mana Djeme Isaac, and Ali Gaston have been involved in their communities in linguistics, language development and translation. They are Moloko speakers and between them they also speak French, Fulfulde, Guiziga, Muyang, and Hausa. Together with the Moloko Language and Translation committees they have produced several books in the Moloko language. Dianne Friesen, a linguist with SIL International, joined them in 1999, studied the language, and helped in producing the books. Together they produced this grammar. It came out of hours spent at friends’ houses hearing and recording stories, hours spent listening to the tapes and transcribing the stories, then translating them and studying the language through them. Time was spent together and with others speaking the language and talking about it, translating resources and talking to people about them. Grammar discoveries were made in the office, in the fields while working, and at gatherings. In the process, the four have become more and more passionate about the Moloko language and are eager to share their knowledge about it with others.}

%\dedication{Change dedication in localmetadata.tex}
\typesetter{Barb Penner, Felix Kopecky}
\proofreader{
Amr Zawawy,
Andreas Hölzl,
Aviva Shimelman,
Bev Erasmus,
Brett Reynolds,
Christian Döhler,
Cormac Anderson,
Daniel Riaño,
Eitan Grossman,
Elizabeth Bogal-Allbritten,
Ezekiel Bolaji,
Gerald Delahunty,
Ikmi Nur Oktavianti,
Jean Nitzke,
Ken Manson,
Lea Schäfer,
Linda Lanz,
Maria Isabel Maldonado,
Michael Rießler,
Myke Brinkerhoff,
Ludger Paschen,
Prisca Jerono,
Steve Pepper,
Varun deCastro-Arrazola
}
\author{Dianne Friesen\xspace\newlineCover with Mana Djeme Isaac, Ali Gaston, and Mana Samuel}
\BookDOI{10.5281/zenodo.824016}%ask coordinator for DOI
\renewcommand{\lsISBNdigital}{978-3-946234-63-0}
\renewcommand{\lsISBNhardcover}{978-3-946234-62-3}
\renewcommand{\lsISBNsoftcover}{978-3-946234-64-7}
\renewcommand{\lsISBNsoftcoverus}{978-1-536924-55-8}
\renewcommand{\lsSeries}{algad} % use lowercase acronym, e.g. sidl, eotms, tgdi
\renewcommand{\lsSeriesNumber}{3} %will be assigned when the book enters the proofreading stage
\renewcommand{\lsURL}{http://langsci-press.org/catalog/book/118} % contact the coordinator for the right number
 